### 2015-08-03 implementation-packages.tex
tweaks to package discussion

In Spack, packages are Python scripts that build software artifacts.
Each package is a class that extends a generic {\tt Package}
base class.  {\tt Package} implements the bulk of the build process, but
subclasses provide their own {\tt install} method to handle the
specifics of particular packages. The subclass does {\it not} have to
handle managing the install location.  Rather, Spack passes the {\tt install}
method a {\tt prefix} parameter.  The package implementer must ensure that
her {\tt install} function installs the package {\it into} the {\tt prefix},
but Spack ensures that {\tt prefix} is computed so that it is
unique for every configuration of a package.  To further simplify
package implementation, Spack implements an embedded domain-specific
language (DSL).
The DSL provides directives, such as {\tt depends\_on},
{\tt version}, {\tt patch}, and {\tt provides}, that add metadata
to the package class.

>>>>

In Spack, packages are Python scripts that build software artifacts.
Each package is a class that extends a generic {\tt Package}
base class.  {\tt Package} implements the bulk of the build process, but
subclasses provide their own {\tt install} method to handle the
specifics of particular packages. The subclass does {\it not} have to
handle managing the install location.  Rather, Spack passes the {\tt install}
method a {\tt prefix} parameter.  The package implementer must ensure that
the {\tt install} function installs the package {\it into} the {\tt prefix},
but Spack ensures that {\tt prefix} is computed so that it is
unique for every configuration of a package.  To simplify package 
implementation further, Spack implements an embedded domain-specific
language (DSL).
The DSL provides directives, such as {\tt depends\_on},
{\tt version}, {\tt patch}, and {\tt provides}, that add metadata
to the package class.
